{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-10-16 paper/tex/sections/results.tex
add progenitor description

In Figure~\ref{fig:progenitor_properties}, we show some properties of the progenitors of the LISA detectable DCOs. The top panel shows the inital primary mass and is plotted on a log-scale. We see that the vast majority of NSNSs are formed with progenitor masses below $15 \unit{M_{\rm \odot}}$ and none are formed with masses greater than $30 \unit{M_{\rm \odot}}$. In contrast,

@@

>>>>

In Figure~\ref{fig:progenitor_properties}, we show some properties of the progenitors of the LISA detectable DCOs. The top panel shows the inital primary mass and is plotted on a log-scale. We see that the vast majority of NSNSs are formed with progenitor masses below $15 \unit{M_{\rm \odot}}$ and none are formed with masses greater than $30 \unit{M_{\rm \odot}}$. In contrast, BHNSs and BHBHs have extremely high primary progenitor masses, particularly given their final BH masses (see Fig.~\ref{fig:fiducial_pdf_distributions}b). These large progenitor masses are often necessary as the high metallicity environment of the Milky Way leads to greater mass loss due to stellar winds and so a greater initial mass is needed to still produce a BH.

The bottom panel of Fig.~\ref{fig:progenitor_properties} shows the initial mass ratio. Overall, we find that the progenitors of detectable systems tend to have more unequal mass ratios compared to the final DCOs (c.f.\ Fig.~\ref{fig:fiducial_pdf_distributions}c). This is because mass loss due to stellar winds tends to bring the mass ratio closer to unity as the systems evolve. Additionally, in contrast to Fig.~\ref{fig:fiducial_pdf_distributions}c, the BHNS distribution is unimodal.

@@

We show the formation channels through which the detectable DCOs formed in
